%%% The main file. It contains definitions of basic parameters and includes all other parts.

%% Settings for single-side (simplex) printing
% Margins: left 40mm, right 25mm, top and bottom 25mm
% (but beware, LaTeX adds 1in implicitly)
\documentclass[12pt,a4paper]{report}
\setlength\textwidth{145mm}
\setlength\textheight{247mm}
\setlength\oddsidemargin{15mm}
\setlength\evensidemargin{15mm}
\setlength\topmargin{0mm}
\setlength\headsep{0mm}
\setlength\headheight{0mm}
% \openright makes the following text appear on a right-hand page
\let\openright=\clearpage

%% Settings for two-sided (duplex) printing
% \documentclass[12pt,a4paper,twoside,openright]{report}
% \setlength\textwidth{145mm}
% \setlength\textheight{247mm}
% \setlength\oddsidemargin{14.2mm}
% \setlength\evensidemargin{0mm}
% \setlength\topmargin{0mm}
% \setlength\headsep{0mm}
% \setlength\headheight{0mm}
% \let\openright=\cleardoublepage

%% Generate PDF/A-2u
\usepackage[a-2u]{pdfx}

%% Character encoding: usually latin2, cp1250 or utf8:
\usepackage[utf8]{inputenc}

%% Prefer Latin Modern fonts
\usepackage{lmodern}

%% Further useful packages (included in most LaTeX distributions)
\usepackage{amsmath}        % extensions for typesetting of math
\usepackage{amsfonts}       % math fonts
\usepackage{amsthm}         % theorems, definitions, etc.
\usepackage{bbding}         % various symbols (squares, asterisks, scissors, ...)
\usepackage{bm}             % boldface symbols (\bm)
\usepackage{graphicx}       % embedding of pictures
\usepackage{fancyvrb}       % improved verbatim environment
\usepackage{natbib}         % citation style AUTHOR (YEAR), or AUTHOR [NUMBER]
\usepackage[nottoc]{tocbibind} % makes sure that bibliography and the lists
			    % of figures/tables are included in the table
			    % of contents
\usepackage{dcolumn}        % improved alignment of table columns
\usepackage{booktabs}       % improved horizontal lines in tables
\usepackage{paralist}       % improved enumerate and itemize
\usepackage{xcolor}         % typesetting in color
\usepackage{natbib}
\usepackage{url}
\usepackage{rotating}
\usepackage{multirow}
\usepackage[capitalize,noabbrev]{cleveref}

%%% Basic information on the thesis

% Thesis title in English (exactly as in the formal assignment)
\def\ThesisTitle{Adapting Pretrained Models for Machine Translation}

% Author of the thesis
\def\ThesisAuthor{Aditya Kurniawan}

% Year when the thesis is submitted
\def\YearSubmitted{2022}

% Name of the department or institute, where the work was officially assigned
% (according to the Organizational Structure of MFF UK in English,
% or a full name of a department outside MFF)
\def\Department{Institute of Formal and Applied Linguistics}

% Is it a department (katedra), or an institute (ústav)?
\def\DeptType{Institute}

% Thesis supervisor: name, surname and titles
\def\Supervisor{doc. RNDr. Ond\r{v}ej Bojar, Ph.D.}

% Supervisor's department (again according to Organizational structure of MFF)
\def\SupervisorsDepartment{Institute of Formal and Applied Linguistics}

% Study programme and specialization
\def\StudyProgramme{Informatics}
\def\StudyBranch{Language Technologies and Computational Linguistics}

% An optional dedication: you can thank whomever you wish (your supervisor,
% consultant, a person who lent the software, etc.)
\def\Dedication{%
First and foremost, I would like to express my sincere gratitude to my supervisors Doc. RNDR. Ond\r{v}ej Bojar, Ph.D from Charles University and Dr Marc Tanti from University of Malta for their overall support, thorough feedback, and guidance during the creation of this thesis.

Secondly, I would like to thank the Erasmus Mundus European Master Program in Language and Communication Technologies (LCT) for the scholarship that allowed me to go through this two-year journey. I am also very thankful to Prof. Markéta Lopatková and Prof. Vladislav Kuboň from Charles University; Prof. Lonneke van Der Plas and Prof. Claudia Borg from the University of Malta; and Dr Bobbye Pernice and Anna Felsing from Universität des Saarlandes for their colossal help in this entire period of study.

Thirdly, I thank MetaCentrum for providing the resources required to complete this thesis. We used the computational resources supplied by the project ``e-Infrastruktura CZ'' (e-INFRA CZ LM2018140), supported by the Ministry of Education, Youth and Sports of the Czech Republic.

Finally, I would also like to thank my family and friends for their support throughout my study.
}

% Abstract (recommended length around 80-200 words; this is not a copy of your thesis assignment!)
\def\Abstract{%
Pre-trained language models received extensive attention in recent years. However, it is still challenging to incorporate a pre-trained model such as BERT into natural language generation tasks. This work investigates a recent method called adapters as an alternative to fine-tuning the whole model in machine translation. Adapters are a promising approach that allows fine-tuning only a tiny fraction of a pre-trained network.
We show that with proper initialization, adapters can help achieve better performance than training models from scratch while training substantially fewer weights than the original model.
We further show that even with randomly set weights used as the base models for fine-tuning, we can achieve similar performance to one of the baseline models, bypassing the need to train hundreds of millions of weights in the pre-training phase.
Furthermore, we study the effectiveness of adapters in the Transformer model for machine translation. We put adapters either in the encoder or the decoder only, and we also attempt to down-scale the pre-trained model size to decrease GPU memory demands.
We found that incorporating adapters in the encoder alone matches the setup's performance when we include the adapters on both the encoder and decoder.
Finally, our down-scaling study found that using only half of the original pre-trained weights can positively impact the performance when fine-tuned with adapters.
}

% 3 to 5 keywords (recommended), each enclosed in curly braces
\def\Keywords{%
% {key} {words}
{adapters} {machine translation} {bert} {transformer} {transfer learning}
}

%% The hyperref package for clickable links in PDF and also for storing
%% metadata to PDF (including the table of contents).
%% Most settings are pre-set by the pdfx package.
\hypersetup{unicode}
\hypersetup{breaklinks=true}

% Definitions of macros (see description inside)
\include{macros}

% Title page and various mandatory informational pages
\begin{document}
\include{title}

%%% A page with automatically generated table of contents of the master thesis

\tableofcontents

%%% Each chapter is kept in a separate file
\include{sections/preface}
\include{sections/chap01}
\include{sections/chap02}
\include{sections/chap03}
\include{sections/chap04-01}
\include{sections/chap04-02}

\include{sections/conclusion}

%%% Bibliography
\include{bibliography}

%%% Figures used in the thesis (consider if this is needed)
\listoffigures

%%% Tables used in the thesis (consider if this is needed)
%%% In mathematical theses, it could be better to move the list of tables to the beginning of the thesis.
\listoftables

%%% Abbreviations used in the thesis, if any, including their explanation
%%% In mathematical theses, it could be better to move the list of abbreviations to the beginning of the thesis.
% \chapwithtoc{List of Abbreviations}

%%% Attachments to the master thesis, if any. Each attachment must be
%%% referred to at least once from the text of the thesis. Attachments
%%% are numbered.
%%%
%%% The printed version should preferably contain attachments, which can be
%%% read (additional tables and charts, supplementary text, examples of
%%% program output, etc.). The electronic version is more suited for attachments
%%% which will likely be used in an electronic form rather than read (program
%%% source code, data files, interactive charts, etc.). Electronic attachments
%%% should be uploaded to SIS and optionally also included in the thesis on a~CD/DVD.
%%% Allowed file formats are specified in provision of the rector no. 72/2017.
\appendix
% \chapter{Attachments}

% \section{First Attachment}

\openright
\end{document}
